Lonely and online: an investigation of social media use and social isolation in China

### 2024-03-19 tandf/Response to reviewers.qmd

---
title: "Response to reviewers"
format: pdf
---

## Reviewer 1

*However, the introduction of the current manuscript should be rewritten. The authors used lots of sentences to describe the background of social media use in China to introduce the research questions. This is unhelpful. It is suggested to examine the related theories to answer, why the phenomenon of social media use in Mainland China may be different from others.*

We introduce the context of China primarily in the Literature Review and Theory section, so we are assuming this is the section to which the reviewer is referring. We agree that the China section is perhaps too long. We have trimmed it and added links to relevant theories.

## Reviewer 2

*1.	In the abstract, there is more information that needs to be added: a clear aim of this research and a few words about the sample size.*

Abstract rewritten and sample size added.

*2.	What is FOMO in abstract? Needs to be clarified here to be understood by the readers.*

Definition added.

*3.	References need to be added in the Introduction section. Also, I suggest merging the introduction section with the literature review and theory section.*

References added. We welcome additional feedback on how to merge the introduction and literature review sections but we believe after deleting the first paragraph of the lit review section, there is a clearer delineation between the two sections.

*4.	In Literature Review and Theory subtitle, the first sentence needs a reference.*

The sentence is deleted as per the comment to point 5 below.

*5.	The second and third sentence in the Literature Review and Theory section (first paragraph) can be moved in the end of the introduction section or can be omitted.*

The sentences have been deleted, additionally, the first sentence read awkwardly without the following sentences and did not add significantly to the section, so we also chose to delete that sentence.

*6.	Reference is needed in the first sentence of the second paragraph in the Literature Review and Theory section.*

The references for this claim was located at the end of the paragraph where the arguments of the authors were described in detail. Though, we can see how it would be confusing. We moved the references to the end of the first sentence.

*7.	Nothing in the literature review about social media addiction. I suggest to see: Social isolation, social support and their relationship with smartphone addiction; examples: The relationship between addiction to smartphone usage and depression among adults: A crosssectional study, Smartphone addiction among university students in the light of some variables, and Examining the effects of motives and gender differences on smartphone addiction.*

*8.	I believe that the testable hypotheses are clear but I suggest to be more in a direct way. Why use “weak or possibly” for example? Why “a strongly”? The results will explain these.*

Fair point. Qualifying words have been removed.

*9.	Also, a clear research question need to be stated in the end of the introduction section.*

We re-wrote the second half of the introduction to clarify our research question and contribution.

*10.	How can the researchers explain that the sample represent ALL China? We know the cultural diversity in a “BIG” China.*

*11.	Need more explanation about the sample. Researchers stated it is random sample. How? Clarification is needed.*

*12.	I suggest that the method section needs to start with sample.*

*13.	No need for the margin in the end of page 5. This information is vital and essential procedures. Need to be moved in the body of the research.*

*14.	Validity and reliability are needed for thew measurements.*

*15.	Sample description is needed in the method section, sample.*

*16.	Figure ?? and Table ?? are  noticed. Need to number the figures and tables.*

This may be a font issue, as our version of the PDF does not contain any missing figure or table numbers, nor does the LaTeX file. Happy to help troubleshoot further but everything on our end looks complete.

### 2024-03-19 tandf/Social Isolation in China.qmd
Revision updates

---
title: "Lonely and online: an investigation of social media use and social isolation in China"
date: '`r format(Sys.time(), "%B %d, %Y")`'
abstract: "Early research and popular discourse on the promise of the internet's impact on social isolation was optimistic. Since these early predictions, research has become less positive, usually pointing to the negative role of social media, withn more recent studies focused on heterogeneous effects. Using data from a nationwide survey of Chinese citizens to gain leverage on this disagreement in the literature, our research finds support for those that have focused on heterogeneous effects - we find that urbancity is a key moderating variable. Additionally, our results lend support to a FOMO mechanism while they are not suggestive of a mechanism by which negative content is the channel through which social media generates feelings of social isolations. Overall, our findings suggest that institutional context may not play an important role in the social media - social isolation relationship."
keywords: [Social Isolation, Social Media, Digital Communication, China]
format:
  tandf-pdf:
    keep-tex: true 
execute: 
  echo: false
  warning: false
keep-tex: true
bibliography: references.bib
csl: taylor-and-francis-apa.csl
---

@@

# Social Isolation in China

@@

Research is quite mixed when it comes to identifying the relationship between social media use and feelings of isolationism. Early research suggested that the internet would build social capital, or an interconnectedness between people, and that social media platforms were the ultimate way to bring people together. Since then, research on the subject has been decidedly more mixed. On one hand, some authors have found social media may encourage social isolation, and ultimately, social media users may feel more disconnected from others than those who do not use social media. On the other hand, others have found that there is only a minimal relationship between these two variables. More recent scholarship has suggested that social media may produce heterogeneous effects on individuals. This study uses the little-studied Chinese social media environment to try and gain leverage on this question - the Chinese online environment has certain features that should both moderate and exacerbate key causal pathways previously identified in the literature. To we employ a large survey of Chinese internet users and test a variety of regression specifications.[^1] The main result is that social media use is generally negatively related to social isolation, though the nature of this relationship changes depending on the urbanicity of the respondent - being in a rural area amplifies this relationship. This finding lends support both to the previous negative relationship findings and also reinforce the findings that emphasize heterogeneous effects.

@@

The existing literature on social isolation and social media use generally finds a negative to null relationship between the two variables, while the most recent research has suggested that social media has heterogeneous effects. Based on this existing literature, we then develop some testable hypotheses regarding how the relationship between usage and isolation may vary in the context of China. The result of these hypotheses tests will help to better understand the possible mechanism that links these two variables.

Initially, scholars imagined that social media would create more opportunities for users to create unique and fulfilling social relationships. The early theorizing about the possible benefits of social media hypothesized three important mechanisms by which social media could decrease loneliness. 1) creating more opportunities for online to offline meetups and 2) helping to alleviate feelings of isolation for those who have difficulty making in-person social connections via joining an online communities, and 3) facilitating keeping in touch with family and friends [@ellison2007; @steinfield2008; @subrahmanyam2008].

@@

Most of the existing research on the subject focuses on Western highly developed societies, and this focus may limit variation on key independent variables given the similar social and institutional context in which users are embedded. To address this problem, this study aims to understand how these complex dynamics interact in the non-Western setting of China. Relatively little is known about China's level of social isolation, though what evidence that does exist suggests that it is on the rise. Twenge et al.'s study found that adolescent feelings of loneliness have generally been on the rise in comparable East Asian countries [@twenge2021]. News reports have highlighted the increasing number of people who consider themselves to be online outcasts or losers (*diaosi*) [@nan2013; @szablewicz2014; @chinas2016]. We do not aim to make a direct comparison between China and Western countries but rather highlight the way in which China's unique context helps shed light on which contextual factors matter in understanding the linkage between the two variables.

The most important of these contextual factor in China is that social media space that is highly controlled online environment. Many people are aware that the Chinese government heavily censors politically sensitive content on online platforms. Fewer are aware that the Chinese government spends as much, if not more, effort to clean up non-political negative or distressing content on the Chinese internet, such as scams, instances of cyber bullying, disturbing videos, and vulgar content [@wang2020]. This control impulse also extends content the government views as spiritually polluting, such as pornography, scantily dressed women, and other escapist content. While the Chinese government and online platforms are not 100 per cent effective in their ability to completely stamp out such content, the default is that such content is actively restricted, while US platforms tent to take a more pro-speech regulatory position [@liu2022]. If one of the main mechanisms through which social media promotes social isolation occurs is exposure to negative content, then this highly regulated online environment should lead to a weaker relationship between social media use and isolation. Suggestive of this is a a study by Liu and Liu that finds Chinese who consumed more commercialized and sensationalized media reported more trauma during the first COVID-19 outbreak in China than those who followed government sources [@liu2020].

@@

-   **H1a:** social media use should have a weak or possibly positive connection to social isolation due to strengthened government control over online content

-   **H1b:** social media use should have a strongly negative connection to social isolation due to the dominance of influencer culture in China, possibly moderated by age.

>>>>

---
title: "Lonely and online: an investigation of social media use and social isolation in China"
date: '`r format(Sys.time(), "%B %d, %Y")`'
abstract: "Research on the link between social media and well being has lead to ambiguous findings - some research has found a positive, negative, and mixed relationship between the two. We employ the case of China, in which social media is controlled in important ways, as a useful alternative case to gain leverage on these ambiguities. Using data from a nationwide survey of Chinese citizens (n=2292), we principally find that individual, heterogeneous effects are an important driver of the relationship between levels of social media use and reported well-being. Additionally, our results lend support to a FOMO (fear of missing out) mechanism as an important driver of the relationship while not finding support for the mechanism of exposure to negative content on social media as a predictor of well-being. Finally, our findings suggest that institutional context may not play an important role in the social media - social isolation relationship."
keywords: [Social Isolation, Social Media, Digital Communication, China]
format:
  tandf-pdf:
    keep-tex: true 
execute: 
  echo: false
  warning: false
keep-tex: true
bibliography: references.bib
csl: taylor-and-francis-apa.csl
shift-heading-level-by: -1
---

@@

@@

Research is quite mixed when it comes to identifying the relationship between social media use and feelings of isolationism. Early research suggested that the internet would build social capital, or an interconnectedness between people, and that social media platforms were the ultimate way to bring people together [@ellison2007]. Since then, research on the subject has been decidedly more mixed [@duradoni2020; @jiménez2022; @valkenburg2022]. On one hand, some authors have found social media may encourage social isolation, and ultimately, social media users may feel more disconnected from others than those who do not use social media. On the other hand, others have found that there is only a minimal relationship between these two variables. More recent scholarship has suggested that social media use may produce heterogeneous effects on individuals' sense of well-being [@ivie2020; @ostic2021].

This study uses the little-studied Chinese social media environment to answer two research questions that remain unresolved in the literature: 1) through which channels or mechanisms do possible heterogeneous effects operate through and 2) how much does internet context change the relationship between social isolation and social media use. The reason that we believe the case of China can be helpful in answering these question is that Chinese online environment has certain features that should both moderate and exacerbate key causal pathways previously identified in the literature. To resolve these debates, we employ a large survey (n=2292) of Chinese internet users and test a variety of regression specifications.[^1] The main result is that social media use is generally negatively related to social isolation, though the nature of this relationship changes depending on the urbanicity of the respondent - being in a rural area amplifies this relationship. These results are consistent with a mechanism that links the two via the harmfulness of being exposed to constant online comparisons (so-called FOMO or fear of missing out). However, the contextual differences of the Chinese internet compared to the Western intern do not appear to significantly alter the relationship.

@@

Initially, scholars imagined that social media would create more opportunities for users to create unique and fulfilling social relationships [@ellison2007; @steinfield2008; @subrahmanyam2008]. The early theorizing about the possible benefits of social media hypothesized three important mechanisms by which social media could decrease loneliness. 1) creating more opportunities for online to offline meetups and 2) helping to alleviate feelings of isolation for those who have difficulty making in-person social connections via joining an online communities, and 3) facilitating keeping in touch with family and friends.

@@

Most of the existing research on the subject focuses on Western highly developed societies, and this focus may limit variation on key independent variables given the similar social and institutional context in which users are embedded. In particular, we believe the case of China can provide leverage in three areas that existing theories have difficulty resolving. The first is that

To address this problem, this study aims to understand how these complex dynamics interact in the non-Western setting of China. Relatively little is known about China's level of social isolation, though what evidence that does exist suggests that it is on the rise. Twenge et al.'s study found that adolescent feelings of loneliness have generally been on the rise in comparable East Asian countries [@twenge2021]. News reports have highlighted the increasing number of people who consider themselves to be online outcasts or losers (*diaosi*) [@nan2013; @szablewicz2014; @chinas2016]. We do not aim to make a direct comparison between China and Western countries but rather highlight the way in which China's unique context helps shed light on which contextual factors matter in understanding the linkage between the two variables.

The most important of these contextual factor in China is that social media space that is highly controlled online environment. Many people are aware that the Chinese government heavily censors politically sensitive content on online platforms. Fewer are aware that the Chinese government spends as much, if not more, effort to clean up non-political negative or distressing content on the Chinese internet, such as scams, instances of cyber bullying, disturbing videos, and vulgar content [@wang2020]. This control impulse also extends content the government views as spiritually polluting, such as pornography, scantily dressed women, and other escapist content. While the Chinese government and online platforms are not 100 per cent effective in their ability to completely stamp out such content, the default is that such content is actively restricted, while US platforms tent to take a more pro-speech regulatory position [@liu2022]. If one of the main mechanisms through which social media promotes social isolation occurs is exposure to negative content, then this highly regulated online environment should lead to a weaker relationship between social media use and isolation. Suggestive of this is a study by Liu and Liu that finds Chinese who consumed more commercialized and sensationalized media reported more trauma during the first COVID-19 outbreak in China than those who followed government sources [@liu2020].

@@

-   **H1a:** social media use should have a positive connection to social isolation due to strengthened government control over online content

-   **H1b:** social media use should have a negative connection to social isolation due to the dominance of influencer culture in China, moderated by age.

### 2024-03-19 tandf/Social-Isolation-in-China.tex
Revision updates

%

%\author{
%\name{A.~N. Author\textsuperscript{a}\thanks{CONTACT A.~N. Author. Email: latex.helpdesk@tandf.co.uk} and John Smith\textsuperscript{b}}
%\affil{\textsuperscript{a}Taylor \& Francis, 4 Park Square, Milton Park, Abingdon, UK; \textsuperscript{b}Institut f\"{u}r Informatik, Albert-Ludwigs-Universit\"{a}t, Freiburg, Germany}
%}

@@

\begin{abstract}
Early research and popular discourse on the promise of the internet's
impact on social isolation was optimistic. Since these early
predictions, research has become less positive, usually pointing to the
negative role of social media, withn more recent studies focused on
heterogeneous effects. Using data from a nationwide survey of Chinese
citizens to gain leverage on this disagreement in the literature, our
research finds support for those that have focused on heterogeneous
effects - we find that urbancity is a key moderating variable.
Additionally, our results lend support to a FOMO mechanism while they
are not suggestive of a mechanism by which negative content is the
channel through which social media generates feelings of social
isolations. Overall, our findings suggest that institutional context may
not play an important role in the social media - social isolation
relationship.
\end{abstract}

\begin{keywords}
    Social Isolation, Social Media, Digital Communication, 
    China
\end{keywords}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, boxrule=0pt, interior hidden, sharp corners, frame hidden, enhanced, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

@@

\hypertarget{social-isolation-in-china}{%
\section{Social Isolation in China}\label{social-isolation-in-china}}

\hypertarget{introduction}{%
\subsection{Introduction}\label{introduction}}

Research is quite mixed when it comes to identifying the relationship
between social media use and feelings of isolationism. Early research
suggested that the internet would build social capital, or an
interconnectedness between people, and that social media platforms were
the ultimate way to bring people together. Since then, research on the
subject has been decidedly more mixed. On one hand, some authors have
found social media may encourage social isolation, and ultimately,
social media users may feel more disconnected from others than those who
do not use social media. On the other hand, others have found that there
is only a minimal relationship between these two variables. More recent
scholarship has suggested that social media may produce heterogeneous
effects on individuals. This study uses the little-studied Chinese
social media environment to try and gain leverage on this question - the
Chinese online environment has certain features that should both
moderate and exacerbate key causal pathways previously identified in the
literature. To we employ a large survey of Chinese internet users and
test a variety of regression specifications.\footnote{All data and
  analysis files for this research are available at the author's
  website.} The main result is that social media use is generally
negatively related to social isolation, though the nature of this
relationship changes depending on the urbanicity of the respondent -
being in a rural area amplifies this relationship. This finding lends
support both to the previous negative relationship findings and also
reinforce the findings that emphasize heterogeneous effects.

\hypertarget{literature-review-and-theory}{%
\subsection{Literature Review and
Theory}\label{literature-review-and-theory}}

The existing literature on social isolation and social media use
generally finds a negative to null relationship between the two
variables, while the most recent research has suggested that social
media has heterogeneous effects. Based on this existing literature, we
then develop some testable hypotheses regarding how the relationship
between usage and isolation may vary in the context of China. The result
of these hypotheses tests will help to better understand the possible
mechanism that links these two variables.

Initially, scholars imagined that social media would create more
opportunities for users to create unique and fulfilling social
relationships. The early theorizing about the possible benefits of
social media hypothesized three important mechanisms by which social
media could decrease loneliness. 1) creating more opportunities for
online to offline meetups and 2) helping to alleviate feelings of
isolation for those who have difficulty making in-person social
connections via joining an online communities, and 3) facilitating
keeping in touch with family and friends (Ellison et al., 2007;
Steinfield et al., 2008; Subrahmanyam et al., 2008).

@@

Most of the existing research on the subject focuses on Western highly
developed societies, and this focus may limit variation on key
independent variables given the similar social and institutional context
in which users are embedded. To address this problem, this study aims to
understand how these complex dynamics interact in the non-Western
setting of China. Relatively little is known about China's level of
social isolation, though what evidence that does exist suggests that it
is on the rise. Twenge et al.'s study found that adolescent feelings of
loneliness have generally been on the rise in comparable East Asian
countries (Twenge et al., 2021). News reports have highlighted the
increasing number of people who consider themselves to be online
outcasts or losers (\emph{diaosi}) (\emph{China{'}s Latest Social Media
Trend}, 2016; Nan, 2013; Szablewicz, 2014). We do not aim to make a
direct comparison between China and Western countries but rather
highlight the way in which China's unique context helps shed light on
which contextual factors matter in understanding the linkage between the
two variables.

The most important of these contextual factor in China is that social
media space that is highly controlled online environment. Many people
are aware that the Chinese government heavily censors politically
sensitive content on online platforms. Fewer are aware that the Chinese
government spends as much, if not more, effort to clean up non-political
negative or distressing content on the Chinese internet, such as scams,
instances of cyber bullying, disturbing videos, and vulgar content
(Wang, 2020). This control impulse also extends content the government
views as spiritually polluting, such as pornography, scantily dressed
women, and other escapist content. While the Chinese government and
online platforms are not 100 per cent effective in their ability to
completely stamp out such content, the default is that such content is
actively restricted, while US platforms tent to take a more pro-speech
regulatory position (J. Liu \& Yang, 2022). If one of the main
mechanisms through which social media promotes social isolation occurs
is exposure to negative content, then this highly regulated online
environment should lead to a weaker relationship between social media
use and isolation. Suggestive of this is a a study by Liu and Liu that
finds Chinese who consumed more commercialized and sensationalized media
reported more trauma during the first COVID-19 outbreak in China than
those who followed government sources (C. Liu \& Liu, 2020).

@@

\begin{itemize}
\item
  \textbf{H1a:} social media use should have a weak or possibly positive
  connection to social isolation due to strengthened government control
  over online content
\item
  \textbf{H1b:} social media use should have a strongly negative
  connection to social isolation due to the dominance of influencer
  culture in China, possibly moderated by age.
\item
  \textbf{H2:} those who are able to use social media to make new
  friends will have lower social isolation scores than those who do not
\item
  \textbf{H3:} the urban/rural divide will produce differential impacts
  in the above hypotheses on the relationship between social media use
  and social isolation
\end{itemize}

\hypertarget{data-measurement-and-descriptives}{%
\subsection{Data, Measurement, and
Descriptives}\label{data-measurement-and-descriptives}}

@@

\hypertarget{results}{%
\subsection{Results}\label{results}}

@@

\hypertarget{conclusion}{%
\subsection{Conclusion}\label{conclusion}}

@@

\hypertarget{references}{%
\subsection{References}\label{references}}

@@

\hypertarget{online-appendix}{%
\subsection{Online Appendix}\label{online-appendix}}

\hypertarget{variable-operationalization}{%
\subsubsection{Variable
Operationalization}\label{variable-operationalization}}

@@

\hypertarget{residual-analysis}{%
\subsubsection{Residual Analysis}\label{residual-analysis}}

>>>>

\author{\name{\textsuperscript{a} and }
\affil{\textsuperscript{a}
\textsuperscript{b}}}

@@

\begin{abstract}
Research on the link between social media and well being has lead to
ambiguous findings - some research has found a positive, negative, and
mixed relationship between the two. We employ the case of China, in
which social media is controlled in important ways, as a useful
alternative case to gain leverage on these ambiguities. Using data from
a nationwide survey of Chinese citizens (n=2292), we principally find
that individual, heterogeneous effects are an important driver of the
relationship between levels of social media use and reported well-being.
Additionally, our results lend support to a FOMO (fear of missing out)
mechanism as an important driver of the relationship while not finding
support for the mechanism of exposure to negative content on social
media as a predictor of well-being. Finally, our findings suggest that
institutional context may not play an important role in the social media
- social isolation relationship.
\end{abstract}

\begin{keywords}
    Social Isolation, Social Media, Digital Communication, 
    China
\end{keywords}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, breakable, enhanced, frame hidden, interior hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners]}{\end{tcolorbox}}\fi

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Research is quite mixed when it comes to identifying the relationship
between social media use and feelings of isolationism. Early research
suggested that the internet would build social capital, or an
interconnectedness between people, and that social media platforms were
the ultimate way to bring people together. Since then, research on the
subject has been decidedly more mixed. On one hand, some authors have
found social media may encourage social isolation, and ultimately,
social media users may feel more disconnected from others than those who
do not use social media. On the other hand, others have found that there
is only a minimal relationship between these two variables. More recent
scholarship has suggested that social media use may produce
heterogeneous effects on individuals' sense of well-being. This study
uses the little-studied Chinese social media environment to try and gain
leverage on this question - the Chinese online environment has certain
features that should both moderate and exacerbate key causal pathways
previously identified in the literature. To resolve these debates, we
employ a large survey (n=2292) of Chinese internet users and test a
variety of regression specifications.\footnote{All data and analysis
  files for this research are available at the author's website.} The
main result is that social media use is generally negatively related to
social isolation, though the nature of this relationship changes
depending on the urbanicity of the respondent - being in a rural area
amplifies this relationship. This finding lends support both to the
previous negative relationship findings and also reinforce the findings
that emphasize heterogeneous effects.

\hypertarget{literature-review-and-theory}{%
\section{Literature Review and
Theory}\label{literature-review-and-theory}}

Initially, scholars imagined that social media would create more
opportunities for users to create unique and fulfilling social
relationships (Ellison et al., 2007; Steinfield et al., 2008;
Subrahmanyam et al., 2008). The early theorizing about the possible
benefits of social media hypothesized three important mechanisms by
which social media could decrease loneliness. 1) creating more
opportunities for online to offline meetups and 2) helping to alleviate
feelings of isolation for those who have difficulty making in-person
social connections via joining an online communities, and 3)
facilitating keeping in touch with family and friends.

@@

Most of the existing research on the subject focuses on Western highly
developed societies, and this focus may limit variation on key
independent variables given the similar social and institutional context
in which users are embedded. In particular, we believe the case of China
can provide leverage in three areas that existing theories have
difficulty resolving. The first is that

To address this problem, this study aims to understand how these complex
dynamics interact in the non-Western setting of China. Relatively little
is known about China's level of social isolation, though what evidence
that does exist suggests that it is on the rise. Twenge et al.'s study
found that adolescent feelings of loneliness have generally been on the
rise in comparable East Asian countries (Twenge et al., 2021). News
reports have highlighted the increasing number of people who consider
themselves to be online outcasts or losers (\emph{diaosi})
(\emph{China{'}s Latest Social Media Trend}, 2016; Nan, 2013;
Szablewicz, 2014). We do not aim to make a direct comparison between
China and Western countries but rather highlight the way in which
China's unique context helps shed light on which contextual factors
matter in understanding the linkage between the two variables.

The most important of these contextual factor in China is that social
media space that is highly controlled online environment. Many people
are aware that the Chinese government heavily censors politically
sensitive content on online platforms. Fewer are aware that the Chinese
government spends as much, if not more, effort to clean up non-political
negative or distressing content on the Chinese internet, such as scams,
instances of cyber bullying, disturbing videos, and vulgar content
(Wang, 2020). This control impulse also extends content the government
views as spiritually polluting, such as pornography, scantily dressed
women, and other escapist content. While the Chinese government and
online platforms are not 100 per cent effective in their ability to
completely stamp out such content, the default is that such content is
actively restricted, while US platforms tent to take a more pro-speech
regulatory position (J. Liu \& Yang, 2022). If one of the main
mechanisms through which social media promotes social isolation occurs
is exposure to negative content, then this highly regulated online
environment should lead to a weaker relationship between social media
use and isolation. Suggestive of this is a study by Liu and Liu that
finds Chinese who consumed more commercialized and sensationalized media
reported more trauma during the first COVID-19 outbreak in China than
those who followed government sources (C. Liu \& Liu, 2020).

@@

\begin{itemize}
\item
  \textbf{H1a:} social media use should have a positive connection to
  social isolation due to strengthened government control over online
  content
\item
  \textbf{H1b:} social media use should have a negative connection to
  social isolation due to the dominance of influencer culture in China,
  moderated by age.
\item
  \textbf{H2:} those who are able to use social media to make new
  friends will have lower social isolation scores than those who do not
\item
  \textbf{H3:} the urban/rural divide will produce differential impacts
  in the above hypotheses on the relationship between social media use
  and social isolation
\end{itemize}

\hypertarget{data-measurement-and-descriptives}{%
\section{Data, Measurement, and
Descriptives}\label{data-measurement-and-descriptives}}

@@

\hypertarget{results}{%
\section{Results}\label{results}}

@@

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

@@

\hypertarget{references}{%
\section{References}\label{references}}

@@

\hypertarget{online-appendix}{%
\section{Online Appendix}\label{online-appendix}}

\hypertarget{variable-operationalization}{%
\subsection{Variable
Operationalization}\label{variable-operationalization}}

@@

\hypertarget{residual-analysis}{%
\subsection{Residual Analysis}\label{residual-analysis}}
